---
title: "R Notebook"
output: html_notebook
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE,
                      message = FALSE)
```
install.packages('Rcpp')
library(Rcpp)


```{r}

library(dplyr)
library(tidyverse)
library(ggplot2)
library(sf)
library(terra)
library(tigris)

```


## Link to "tigris" library documentation:
https://cran.r-project.org/web/packages/tigris/tigris.pdf


## Load US Census TIGER/Line Shapefiles at tract level for the entire US
```{r}
#tracts(state = NULL, county = NULL, cb = FALSE, year = NULL, ...)
us_census_tracts_2019 <- tracts(state = NULL, cb = TRUE)
st_crs(us_census_tracts_2019)

```                   



## Load US Census TIGER/Line Shapefiles at tract level for Rhode Island
```{r}

ri_census_tracts_2018 <- tracts(state = "RI", cb = FALSE, year = 2018)
st_crs(ri_census_tracts_2018)

```


## Read in SEPHER dataset (.CSV)
```{r}

#df_sepher_ri <- read.csv('/Users/tomislav_galjanic/Documents/Tomislav/Columbia/Courses/Fall 2021/ENGI E4800/Tedesco/SEPHER 2.0/sepher2.0_cleaned_ri.csv', colClasses = "character")

df_sepher <- read.csv('/Users/tomislav_galjanic/Documents/Tomislav/Columbia/Courses/Fall 2021/ENGI E4800/Tedesco/SEPHER 2.0/sepher2.0_cleaned.csv', colClasses = "character")

```


```{r}

rowSums(!is.na(df_sepher_ri[238, ]))

```


## Join "sf data.frame" with census tract geospatial data with SEPHER data.frame
```{r}

#df_sepher_ri_geo <- right_join(ri_census_tracts_2018, df_sepher_ri, by = c("GEOID" = "FIPS"))

df_sepher_geo <- right_join(us_census_tracts_2019, df_sepher, by = c("GEOID" = "FIPS"))

```



```{r}

no_geoid_match <- df_sepher_ri_geo[is.na(df_sepher_ri_geo$INTPTLAT), ]


```


## Save "sf data.frame" with SEPHER and geospatial data as a .SHP or .GPKG file
```{r}
root_dir <- "/Users/tomislav_galjanic/Documents/Tomislav/Columbia/Courses/Fall 2021/ENGI E4800/Tedesco/SEPHER 2.0/Shape Files"

#st_write(obj = df_sepher_ri_geo, dsn = paste0(root_dir, "/", "sepher_ri_geo.shp") )

st_write(obj = df_sepher_ri_geo, dsn = paste0(root_dir, "/", "sepher_ri_geo.gpkg"), layer = "sepher_ri_geo.gpkg", driver = "GPKG")

```


## Read in (test) "sf data.frame" with SEPHER and geospatial data as a .SHP or .GPKG file
```{r}

#df_ri_read = st_read(system.file("shape/nc.shp", package="sf"))

df_ri_read = st_read(dsn = paste0(root_dir, "/", "sepher_ri_geo.gpkg"), layer = "sepher_ri_geo.gpkg")
str(df_ri_read)

```

